\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/learning_action_models.tex
Update Dec 25 21:20

The logical inference process our approach is based on has trouble learning preconditions that are not, simultaneously, negative effects as well, since in this case no change can be observed between the pre-state and post-state of an action. This is specially the case for static predicates that never change and, hence, can only be preconditions. In order to address this shortcoming, we apply a post-process based on the one proposed in \cite{kuvcera2018louga}. In their proposal, they obtain a full trace by applying the sequence of actions of the input trace and infering the preconditions from this fully observable trace. In our case, since the sequence of actions of the input trace might not be fully observable, we produce the traces by applying the actions found in the validation part of the solution plan. For instance, in the example of the figure \ref{fig:plan-lplan}, the sequence of actions used to produce the full trace would be {\tt{\small(unstack blockB blockA)}}, {\tt{\small(put-down blockB)}}, {\tt{\small(pick-up blockA)}}, and {\tt{\small(stack blockA blockB)}}. This post-process allows \FAMA to learn more complete lists of preconditions and deal with the always problematic static predicates.

>>>>

The logical inference process our approach is based on has trouble learning preconditions that do not appear as negative effects since in this case no change is observed between the pre-state and post-state of an action. This is specially relevant for static predicates that never change and, hence, only appear as preconditions in the actions. In order to address this shortcoming \textcolor[rgb]{1.00,0.00,0.00}{and complete the list of learned preconditions}, we apply a post-process based on the one proposed in~\cite{kuvcera2018louga}. \textcolor[rgb]{1.00,0.00,0.00}{The idea lies in going through every action and counting the number of cases where a literal is present before the action is executed and the number of cases where it is not present. If a literal is present in all the cases before the action, the literal is considered to be a precondition.}

\textcolor[rgb]{1.00,0.00,0.00}{In order to obtain a complete trace, the proposal in ~\cite{kuvcera2018louga} applies the sequence of actions of the input trace and infers the preconditions from this \FO action sequence}. In our case, since the sequence of actions of the input trace might not be fully observable, we produce the traces by applying the actions found in the validation part of the solution plan. For instance, in the example of the figure \ref{fig:plan-lplan}, the sequence of actions used to produce the complete trace would be {\tt{\small(unstack blockB blockA)}}, {\tt{\small(put-down blockB)}}, {\tt{\small(pick-up blockA)}}, and {\tt{\small(stack blockA blockB)}}.

%This post-process allows \FAMA to learn more complete lists of preconditions and deal with the always problematic static predicates.
